%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Shrukul Habib} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Date of Birth} \> June 15, 1995 \\ % Date of birth 
{\bf Nationality} \> Indian % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +91 8904-8907-54 \\ % Mobile phone
{\bf Email} \> {shrukul99@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

Computer Science Engineering student pursuing Final year Bachelor Degree. \\
Passionate about Science, with strong technical, business, and interpersonal skills for working 
in a team. Highly motivated and eager to learn new technologies. \\
\\
Special interests in Operating Systems, Kernel Development, Web Development,
Open Source, Android.

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{Objective}

To contribute as a team member in a lively work environment that will enrich my
skill set too.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2013 -} \> {\bf National Institute of Technology Karnataka, Surathkal} \\[5pt]
\bf{Present}
\>B.Tech in Computer Science \\
\>CGPA - 8.51\\
\>\+
}


%------------------------------------------------

\tabbedblock{
\bf{2011 - 2013} \> {\bf Chetan Pre-University Science College, Hubli} \\[5pt]
\>Pre University Science \\
\>Percentage - 94.3\% \\
\>\+
}

%------------------------------------------------

\tabbedblock{
\bf{2011} \> {\bf Lions English Medium School, Hubli} \\[5pt]
\>Class X \\
\>Percentage - 96.8\% \\
\>\+
}


%------------------------------------------------

%\tabbedblock{
%\bf{2001-2003} \> Advanced Secondary Education - \href{http://www.berkeleycollege.edu}{Berkeley College, California}\\[5pt]
%\>\+
%\textit{Pure Mathematics} \> A \\
%\textit{Statistics (AS)} \> A \\
%\textit{Physics} \> A \\
%\textit{Economics} \> B
%}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\job
{May 2016 -}{July 2016}
{Myntra Designs, Bangalore}
{http://www.myntra.com}
{Retail-Tech Intern}

\begin{itemize}
\item {As part of the Retail-Tech, developed an utility for Cashback Points and also for credit/debit of Loyalty Points.}
\item{Code had to be highly efficient and Failsafe as it was monetary-sensitive.}
\item {Also worked on Myntra's new User Identity Model}
\item{Used NodeJS for backend and ReactJS \& Redux for Frontend Framework.}
\item{Has been put into production and is currently in use.}
\end{itemize}

\job
{May 2015 -}{July 2015}
{IIT Madras, Chennai}
{http://www.iitm.ac.in}
{Research Intern}

\begin{itemize}
\item {Worked on initial draft of Project Vault, a micro-SD sized device which helps in Encrytpion. Tested it on emulator.}
\item{Compiled simple Linux Kernel Modules for Native Hardware. Worked on reducing the Kernel size and reduced the size from 6.8 MB to 3.2 MB.}
\end{itemize}

%------------------------------------------------

\section{Projects}

\begin{itemize}
\item{\bf Android OS Development} \\
\\
Compiled and ported Android Kitkat to Samsung Galaxy Grand Quattro. Used Open-Source Cyanogenmod Project for the same. \\

\item{\bf Natural Language Processing} \\
\\
Created a product Profiling chrome extension which used Natural Language Processing to rate \\
products based on Text Reviews. Implemented in Python. \\

\item{\bf Computer Graphics} \\
\\
Implemented Video Synchronization proposed by Disney and made improvements in the algorithm for Low Quality Videos. Implemented in Python. \\

\item{\bf Image Steganography} \\
\\
Implemented Data Hiding using LSB Algorithm on Images as part of Information Security Course.
Made use of JAVA. \\

\item{\bf Technique for Order of Preference by Similarity To Ideal Solution (TOPSIS)} \\
\\
Collaborated with prof. B.R. Chandavarkar (CSE dept. NITK) and created GUI for “multi-criteria decision making” software which gives an optimal solution to a specific problem having multiple criteria. Built using JAVA. \\

\item{\bf BuStop} \\
\\
BuStop is an Online Bus Ticket booking application created as part of Course Requirement. Created Android Application using Android Studio. \\

\item{\bf Internship Website} \\
\\
Created an Internship Portal as part of Course Requirement. Website built on PHP backend and uses HTML, CSS, Bootstrap  and JavaScipt. \\
\\

\end{itemize}

%----------------------------------------------------------------------------------------
%	Specific Highlights
%----------------------------------------------------------------------------------------

\section{Specific Highlights}
\begin{itemize}
\item{\bf Wayfoo} \\
\\
Created an App for Advanced reservation of tables and menu at select restaurants in and around Bangalore. This is at an advanced stage of implementation. \\

\item{\bf BucksBuddy} \\
\\
Created an App for cashless transactions at establishments situated within the campus. \\
\end{itemize}


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{C, C++}\\
\textit{JAVA}\\
\textit{PHP}\\
\textit{Python}
}

%------------------------------------------------

\skillgroup{Web Development}
{
\textit{HTML5, CSS3, JavaScript}\\
\textit{AngularJS, NodeJS}\\
\textit{ReactJS, Redux}\\
}

%------------------------------------------------

\skillgroup{Operating Systems}
{
\textit{Windows}\\
\textit{Linux}\\
\textit{OS X \\}\\
}

%------------------------------------------------

\skillgroup{Tools}
{
\textit{Android Studio}\\
\textit{\LaTeX}\\
\textit{adb}\\
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Android App and OS Development} \\
\textit{Google App Engine} - Hosting Backend and API's on Google Servers\\
\textit{MySQL Server}\\
\textit{git} - version control system
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\begin{itemize}
\item{Badminton, Football, Running, Cycling, Cricket}
\item{Travelling}
\item{Electronic Gadgets}
\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULARS
%----------------------------------------------------------------------------------------

\section{Extra Curriculars}
\begin{itemize}
\item{Executive Member at IEEE, NITK} 
\item{Participated in District-Level Badminton Tournament} 
\item{Won Scotland Yard 2013, NITK} 
\end{itemize}


%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}

\begin{itemize}
\item{English - Fluent} 
\item{Kannada - Native} 
\item{Hindi   - Fluent} 
\end{itemize}

%----------------------------------------------------------------------------------------

\end{document}